Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-02-17 manuscript-figures.Rmd
preliminary figures for R0, Topt with uncertainty

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp) #nec
library(reshape2) #nec
library(cowplot)
library(viridis)
library(RColorBrewer) #nec
library(MetBrewer)
library(here)
library(lemon)  #nec
library(zplyr) # only needed for placing text using absolute coordinates in contact comparison figure

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp) #nec
library(reshape2) #nec
library(cowplot) #nec
library(viridis) #nec
library(RColorBrewer) #nec
library(MetBrewer) #nec
library(here)
library(lemon)  #nec
library(zplyr) # only needed for placing text using absolute coordinates in contact comparison figure
